#Course Project 1  

```{r,include=FALSE}
library(readxl)
library(dplyr)
library(tidyverse)
setwd("~/Desktop/RR")

```

loading the data 

```{r, echo=TRUE}
data <- read.csv("activity.csv")  
```

Total Steps Each Day
```{r, echo=TRUE}

steps_by_day <- aggregate(steps ~ date, data, sum)
hist(steps_by_day$steps, main = paste("Total Steps Each Day"), col="blue",xlab="Number of Steps")
rmean <- mean(steps_by_day$steps)
rmean
rmedian <- median(steps_by_day$steps)
rmedian
```
* mean: 10766.19 
* median: 10765  

What is the average daily activity pattern?
```{r, echo=TRUE}
steps_by_interval <- aggregate(steps ~ interval, data, mean)
plot(steps_by_interval$interval,steps_by_interval$steps, type="l", xlab="Interval", ylab="Number of Steps",main="Average Number of Steps per Day by Interval")
max_interval <- steps_by_interval[which.max(steps_by_interval$steps),1]
max_interval
```
* Interval with most steps: 835  

Imputing missing values  

```{r, echo=TRUE}
NATotal <- sum(!complete.cases(data))
NATotal
```
* 2304 NA

```{r, echo=TRUE}
StepsAverage <- aggregate(steps ~ interval, data = data, FUN = mean)
fillNA <- numeric()
for (i in 1:nrow(data)) {
    obs <- data[i, ]
    if (is.na(obs$steps)) {
        steps <- subset(StepsAverage, interval == obs$interval)$steps
    } else {
        steps <- obs$steps
    }
    fillNA <- c(fillNA, steps)
}

new_activity <- data
new_activity$steps <- fillNA
```

histogram of the total number of steps taken each day 
```{r, echo=TRUE}
StepsTotalUnion <- aggregate(steps ~ date, data = new_activity, sum, na.rm = TRUE)
hist(StepsTotalUnion$steps, main = paste("Total Steps Each Day"), col="blue", xlab="Number of Steps")
#Create Histogram to show difference. 
hist(steps_by_day$steps, main = paste("Total Steps Each Day"), col="green", xlab="Number of Steps", add=T)
legend("topright", c("Imputed", "Non-imputed"), col=c("blue", "green"), lwd=10)
rmeantotal <- mean(StepsTotalUnion$steps)
rmeantotal
rmediantotal <- median(StepsTotalUnion$steps)
rmediantotal
```
* mean:10766.19
* median: 10766.19

Do these values differ from the estimates from the first part of the assignment?  
```{r, echo=TRUE}
rmeandiff <- rmeantotal - rmean
rmeandiff

rmediandiff <- rmediantotal - rmedian
rmediandiff
```
* In the mean no but in the median they differ in 1.188679
* The impact is that now there is more data in the 10000 - 150000 step interval and changes frequency from 27.5 to 35  

Are there differences in activity patterns between weekdays and weekends?
```{r, echo=TRUE}
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", 
              "Friday")
new_activity$dow = as.factor(ifelse(is.element(weekdays(as.Date(new_activity$date)),weekdays), "Weekday", "Weekend"))
StepsTotalUnion <- aggregate(steps ~ interval + dow, new_activity, mean)
library(lattice)
xyplot(StepsTotalUnion$steps ~ StepsTotalUnion$interval|StepsTotalUnion$dow, main="Average Steps per Day by Interval",xlab="Interval", ylab="Steps",layout=c(1,2), type="l")


```




